\documentclass[aspectratio=169,xcolor=x11names,compress]{beamer}

\useoutertheme[subsection=false,shadow]{miniframes}
\useinnertheme{default}
\usefonttheme{serif}
\usepackage{palatino}

\definecolor{uqamblue}{RGB}{0,53,137}
\setbeamercolor*{lower separation line head}{bg=uqamblue} 
\setbeamercolor*{normal text}{fg=black,bg=white} 
\setbeamercolor*{alerted text}{fg=red} 
\setbeamercolor*{example text}{fg=black} 
\setbeamercolor*{structure}{fg=black} 
 
\setbeamercolor*{palette tertiary}{fg=black,bg=black!10} 
\setbeamercolor*{palette quaternary}{fg=black,bg=black!10}

\setbeamercolor*{itemize item}{fg=uqamblue}

\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[french]{babel}
%\usepackage[latin1]{inputenc}
%\usepackage[english]{babel}
\usepackage{amsfonts,amsmath,amssymb,amsthm,amsrefs}
\usepackage{mathrsfs}
%\usepackage{epsf, subfigure, verbatim}
\usepackage{latexsym}
\usepackage{layout}
\usepackage{dsfont}
\usepackage{xcolor}

\usepackage{graphicx}
\usepackage{caption}
\setbeamertemplate{caption}[numbered]
\usepackage{hyperref}

\usepackage{ragged2e}
\justifying

\usepackage{tcolorbox}
\tcbuselibrary{theorems}
\newtcbtheorem{mytheorem}{Théorème}{colback = blue!10, colframe = uqamblue, fonttitle = \bfseries}{thm}
\newtcbtheorem{myprop}{Proposition}{colback = green!10, colframe = green!50!black, fonttitle = \bfseries}{prop}
\newtcbtheorem{mydef}{Définition}{colback = orange!10, colframe = orange!50!black, fonttitle = \bfseries}{def}
\newtcbtheorem{myhypo}{Hypothèse}{colback = yellow!10, colframe = yellow!50!black, fonttitle = \bfseries}{def}
\setbeamertemplate{theorems}[numbered]

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{systblock} = [rectangle, rounded corners, text centered, draw=black, fill=white, text width=2cm, thick, minimum height=1.8cm]
\tikzstyle{around} = [rectangle, draw=none, fill=none]
\tikzstyle{arrow} = [thick,->,>=stealth]

\newcommand{\intd}{\,\mathrm{d}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\renewcommand{\qedsymbol}{$\blacksquare$}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\nats}{\mathbb{N}}
\newcommand{\ind}{\mathds{1}}


\title{Customer Lifetime Value}
\author{}
\institute{}    
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\section{Introduction \& team picture}

\section{Recap of context \& problem}

\begin{frame}
\frametitle{Why Insurance Companies Should Care About CLV}

\begin{itemize}
  \item \textbf{Providing Insights in a Complex Industry:}
  \begin{itemize}
    \item Insurance operations involve numerous variables, from risk assessment to customer behavior.
    \item \textbf{Customer Lifetime Value} (or CLV) offers a comprehensive metric encompassing these factors.
  \end{itemize}
  
  \item \textbf{Efficient Decision-Making:}
  \begin{itemize}
    \item CLV consolidates diverse information, streamlining decision processes.
    \item Enables optimized resource allocation, customer engagement, and tailored product offerings.
  \end{itemize}
\end{itemize}

\end{frame}


\begin{frame}
\frametitle{What is CLV?}

\begin{itemize}
    \item CLV represents the total expected profit a
    company expects from a client throughout their entire relationship. \pause
    \item Used in multiple industries in order to evaluate the financial value of a
    customer and better tailor the approach of the company towards
    customers (pricing, marketing, etc.) 

\item Mathematically, we can define CLV as
\[
CLV = \E[\sum_{t=1}^T \gamma^t Profit(S_t)]
\]
where:
\begin{itemize}
    \item $\gamma$ is a discounting factor to account for time-value of money.
    \item $Profit(S_t)$ is a function that gives the expected profit from a client given their state $S_t$.
\end{itemize}

\end{itemize}

\end{frame}

\section{Proposed Method}

\begin{frame}
\frametitle{Why Markovian approach?}
\end{frame}

\begin{frame}
\frametitle{Method: overview}
\end{frame}

\begin{frame}
\frametitle{Method: details (1/2)}
\end{frame}

\begin{frame}
\frametitle{Method: details (2/2)}
\end{frame}

\section{Results}

\begin{frame}
\frametitle{Our Results}
\end{frame}

\section{Discussion}

\begin{frame}
\frametitle{Other approaches}

\textbf{Other classification methods}

\begin{itemize}
    \item One limitation of a classification tree is that it is very sensitive to small changes of a variable of interest.
    \item Another option for this supervised classification problem could be to apply a robust logistic regression.
    \item The main advantage of the tree over this regression method is that it can easily deal with outliers and does not require normalization and scaling of data.
\end{itemize}

\textbf{Deep Learning}

\begin{itemize}
    \item A master's thesis was written which attempted to apply deep learning to calculate CLV with a P$\&$C insurance company
    \item 
    \item (link to reference)
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Other approaches}

\textbf{Extended Pareto/NBD Model}

\begin{itemize}
  \item Combines \textbf{Pareto/NBD} and \textbf{Gamma-Gamma} models.
  
  \item \textbf{Pareto/NBD Model}:
  \begin{itemize}
    \item Uses k-means to separate the data set into non-overlapping groups that do not need to be pre-specified.
    \item Uses two main components: Pareto distribution and Negative Binomial Distribution.
    \item Estimates parameters that describe customer behavior, such as transaction rate and the expected number of future transactions.
  \end{itemize}
  
  \item \textbf{Gamma-Gamma Model}:
  \begin{itemize}
    \item Assumes that customer transaction values follow a gamma distribution.
    \item Estimates parameters for average and variability in transaction values.
  \end{itemize}
  
  \item Gives \textbf{CLV predictions} by multiplying results from both submodels.
  
  \item Challenges Faced:
  \begin{itemize}
    \item Attempted implementation, but faced technical hurdles.
    \item The dataset provided for the workshop was not suited for implementation (missing variables).
  \end{itemize}
\end{itemize}

\end{frame}


\end{document}
